---
title: "final_project_attrition_gable"
author: "Kyle Gable"
date: 2023-04-22
output:
  html_document:
    df_print: paged
---

# An Introduction
This analysis will investigate the important variables that contribute to the loss of employees (employee attrition) and seeks to answer the question of “What variables play an important role in employee attrition rates?” By utilizing various ML methods, one can hope to obtain a better understanding of the important variables that contribute to employee attrition (Attrition_Status). The objective of this analysis is to identify what variables are important in the prediction of employee attrition (Attrition_Status), if any.

# Data Prep
Reading in the data:
```{r CSVReading}
library(readr)
attrition <- read_csv("data/turnover.csv")

```

Using `str` and `summary` to get a preliminary look at the data:
```{r Preliminary}
str(attrition)
summary(attrition)
```

Converting categorical and binary variables to factors:
```{r Factoring}
attrition$Attrition_Status <- as.factor(attrition$Attrition_Status)
attrition$Gender <- as.factor(attrition$Gender)
attrition$Employee_Industry <- as.factor(attrition$Employee_Industry)
attrition$Employee_Profession <- as.factor(attrition$Employee_Profession)
attrition$Source_of_Hire <- as.factor(attrition$Source_of_Hire)
attrition$Coach <- as.factor(attrition$Coach)
attrition$Head_Supervisor_Gender <- as.factor(attrition$Head_Supervisor_Gender)
attrition$Wage_Color <- as.factor(attrition$Wage_Color)
attrition$Way_to_Work <- as.factor(attrition$Way_to_Work)
str(attrition)
summary(attrition)
```

Cleansing the dataset:
```{r Cleansing}
attrition_cleansed <- subset(attrition, Employee_Age != 30.40033257)
str(attrition_cleansed)
summary(attrition_cleansed)
```

## Partitioning the dataset into training and validation/test datasets

Loading in libraries:
```{r Libraries}
library(dplyr)
library(ggplot2)
library(caret)
library(MLmetrics)
library(GGally)
library(coefplot)
```

Partitioning the data:
```{r Parition}
set.seed(100)
attrition_cleansed_intraining <- createDataPartition(y = attrition_cleansed$Attrition_Status,
  p = .70,
  list = FALSE)

attrition_cleansed_training <- attrition_cleansed[attrition_cleansed_intraining,]
attrition_cleansed_validation <- attrition_cleansed[-attrition_cleansed_intraining,]
```

## EDA

Creating plots and tabular summaries to explore the variables and see how they might be related:
```{r EDA}
attrition_cleansed_training_LM <- glm(formula = Attrition_Status ~ Experience_in_Months + Employee_Age + Extraversion + Agreeableness + Conscientiousness + Neuroticism + Openness + Gender + Employee_Profession + Employee_Industry + Source_of_Hire + Coach + Head_Supervisor_Gender + Way_to_Work + Wage_Color,
                data = attrition_cleansed_training,
                family = binomial)

summary(attrition_cleansed_training_LM)

attrition_cleansed_training_cor <- cor(as.data.frame(attrition_cleansed_training[, unlist(lapply(attrition_cleansed_training, is.numeric))]))
cor(as.data.frame(attrition_cleansed_training[, unlist(lapply(attrition_cleansed_training, is.numeric))]))

attrition_cleansed_training_LM %>% ggpairs(columns = c("Employee_Age", "Extraversion", "Agreeableness", "Conscientiousness", "Neuroticism", "Openness"),
                                           progress = FALSE)
attrition_cleansed_training_LM %>% ggpairs(columns = c("Employee_Age", "Extraversion", "Agreeableness", "Conscientiousness", "Neuroticism", "Openness"),
                                           progress = FALSE) + scale_x_log10()
attrition_cleansed_training_LM %>% ggpairs(columns = c("Employee_Age", "Extraversion", "Agreeableness", "Conscientiousness", "Neuroticism", "Openness"),
                                           progress = FALSE) + scale_x_sqrt()
coefplot(attrition_cleansed_training_LM, predictors=c("Employee_Age", "Extraversion", "Agreeableness", "Conscientiousness", "Neuroticism", "Openness", "Gender", "Employee_Industry", "Source_of_Hire", "Coach", "Head_Supervisor_Gender", "Way_to_Work", "Wage_Color"), sort = c("alphabetical"))
```
Looking at the coefficient values themselves INCLUDING for Employee_Profession (Employee_Profession being added to the visual above adds a problem that I could not fix regarding Employee_ProfessionTeaching):
```{r Coef}
coef(attrition_cleansed_training_LM)
```

## Fitting regression models:

```{r Regression_Models}
attrition_cleansed_training_all_variables <- glm(formula = Attrition_Status ~ Experience_in_Months + Employee_Age + Extraversion + Agreeableness + Conscientiousness + Neuroticism + Openness + Gender + Employee_Profession + Employee_Industry + Source_of_Hire + Coach + Head_Supervisor_Gender + Way_to_Work + Wage_Color,
                data = attrition_cleansed_training,
                family = binomial)

attrition_cleansed_training_significant <- glm(formula = Attrition_Status ~ Experience_in_Months + Source_of_Hire + Way_to_Work,
                data = attrition_cleansed_training,
                family = binomial)

attrition_cleansed_training_feeling1 <- glm(formula = Attrition_Status ~ Experience_in_Months + Employee_Profession + Employee_Industry + Source_of_Hire + Way_to_Work,
                data = attrition_cleansed_training,
                family = binomial)

attrition_cleansed_training_feeling2 <- glm(formula = Attrition_Status ~ Experience_in_Months + Extraversion + Agreeableness + Conscientiousness + Employee_Profession + Employee_Industry + Source_of_Hire + Way_to_Work,
                data = attrition_cleansed_training,
                family = binomial)

attrition_cleansed_training_feeling3 <- glm(formula = Attrition_Status ~ Experience_in_Months + Employee_Age + Extraversion + Agreeableness + Conscientiousness + Neuroticism + Gender + Employee_Profession + Employee_Industry + Source_of_Hire + Way_to_Work + Wage_Color,
                data = attrition_cleansed_training,
                family = binomial)
```

### Assessing model fit on training data

```{r Model_fit}
AIC_Values <- c(summary(attrition_cleansed_training_all_variables)$aic,
  summary(attrition_cleansed_training_significant)$aic,
  summary(attrition_cleansed_training_feeling1)$aic,
  summary(attrition_cleansed_training_feeling2)$aic,
  summary(attrition_cleansed_training_feeling3)$aic)

AIC_Values
```

### Using the models to make predictions on the validation data

```{r Predictions}
Predict1 <- predict(attrition_cleansed_training_all_variables, newdata = attrition_cleansed_validation, type = "response") 
Predict2 <- predict(attrition_cleansed_training_significant, newdata = attrition_cleansed_validation, type = "response")
Predict3 <- predict(attrition_cleansed_training_feeling1, newdata = attrition_cleansed_validation, type = "response") 
Predict4 <- predict(attrition_cleansed_training_feeling2, newdata = attrition_cleansed_validation, type = "response")
Predict5 <- predict(attrition_cleansed_training_feeling3, newdata = attrition_cleansed_validation, type = "response")
head(Predict1, 2)
head(Predict2, 2)
head(Predict3, 2)
head(Predict4, 2)
head(Predict5, 2)
```
> Personal Note: Above is the predicted probability that each observation will have an Attrition_Status of "1."

#### Fitting a null model

```{r Nulls}
# Create a vector of 0's
Training_null <- rep(0, nrow(attrition_cleansed_training))
Validation_null <- rep(0, nrow(attrition_cleansed_validation))

cm_training_null <- caret::confusionMatrix(as.factor(Training_null), attrition_cleansed_training$Attrition_Status, positive="1")
cm_training_null

cm_validation_null <- caret::confusionMatrix(as.factor(Validation_null), attrition_cleansed_validation$Attrition_Status, positive="1")
cm_validation_null
```

#### Fitting logistic regression models

```{r Logistic_Regression_Training_Models}
# Fitting models
lr_training_all_variables <- glm(Attrition_Status ~ Experience_in_Months + Employee_Age + Extraversion + Agreeableness + Conscientiousness + Neuroticism + Openness + Gender + Employee_Profession + Employee_Industry + Source_of_Hire + Coach + Head_Supervisor_Gender + Way_to_Work + Wage_Color,
                        data=attrition_cleansed_training,
                        family=binomial(link="logit"))
lr_training_significant <- glm(Attrition_Status ~ Experience_in_Months + Source_of_Hire + Way_to_Work,
                        data=attrition_cleansed_training,
                        family=binomial(link="logit"))
lr_training_feeling1 <- glm(Attrition_Status ~ Experience_in_Months + Employee_Profession + Employee_Industry + Source_of_Hire + Way_to_Work,
                        data=attrition_cleansed_training,
                        family=binomial(link="logit"))
lr_training_feeling2 <- glm(Attrition_Status ~ Experience_in_Months + Extraversion + Agreeableness + Conscientiousness + Employee_Profession + Employee_Industry + Source_of_Hire + Way_to_Work,
                        data=attrition_cleansed_training,
                        family=binomial(link="logit"))
lr_training_feeling3 <- glm(Attrition_Status ~ Experience_in_Months + Employee_Age + Extraversion + Agreeableness + Conscientiousness + Neuroticism + Gender + Employee_Profession + Employee_Industry + Source_of_Hire + Way_to_Work + Wage_Color,
                        data=attrition_cleansed_training,
                        family=binomial(link="logit"))

## Converting fitted model values into fitted classes
yhat_lr_training_all_variables <- (lr_training_all_variables$fit > 0.5) * 1
yhat_lr_training_significant <- (lr_training_significant$fit > 0.5) * 1
yhat_lr_training_feeling1 <- (lr_training_feeling1$fit > 0.5) * 1
yhat_lr_training_feeling2 <- (lr_training_feeling2$fit > 0.5) * 1
yhat_lr_training_feeling3 <- (lr_training_feeling3$fit > 0.5) * 1

fitted_class_lr_training_all_variables <- data.frame(as.factor(lr_training_all_variables$y), as.factor(yhat_lr_training_all_variables))
names(fitted_class_lr_training_all_variables) <- c("yact", "yhat")
fitted_class_lr_training_significant <- data.frame(as.factor(lr_training_significant$y), as.factor(yhat_lr_training_significant))
names(fitted_class_lr_training_significant) <- c("yact", "yhat")
fitted_class_lr_training_feeling1 <- data.frame(as.factor(lr_training_feeling1$y), as.factor(yhat_lr_training_feeling1))
names(fitted_class_lr_training_feeling1) <- c("yact", "yhat")
fitted_class_lr_training_feeling2 <- data.frame(as.factor(lr_training_feeling2$y), as.factor(yhat_lr_training_feeling2))
names(fitted_class_lr_training_feeling2) <- c("yact", "yhat")
fitted_class_lr_training_feeling3 <- data.frame(as.factor(lr_training_feeling3$y), as.factor(yhat_lr_training_feeling3))
names(fitted_class_lr_training_feeling3) <- c("yact", "yhat")

# Creating & displaying confusion matrices
cm_train_lr_training_all_variables <- confusionMatrix(fitted_class_lr_training_all_variables$yact, fitted_class_lr_training_all_variables$yhat, positive="1")
cm_train_lr_training_significant <- confusionMatrix(fitted_class_lr_training_significant$yact, fitted_class_lr_training_significant$yhat, positive="1")
cm_train_lr_training_feeling1 <- confusionMatrix(fitted_class_lr_training_feeling1$yact, fitted_class_lr_training_feeling1$yhat, positive="1")
cm_train_lr_training_feeling2 <- confusionMatrix(fitted_class_lr_training_feeling2$yact, fitted_class_lr_training_feeling2$yhat, positive="1")
cm_train_lr_training_feeling3 <- confusionMatrix(fitted_class_lr_training_feeling3$yact, fitted_class_lr_training_feeling3$yhat, positive="1")

cm_train_lr_training_all_variables
cm_train_lr_training_significant
cm_train_lr_training_feeling1
cm_train_lr_training_feeling2
cm_train_lr_training_feeling3
```

Making predictions on the validation set data:
```{r Logistic_Regression_Prediction}
pred_lr_all_variables <- predict(lr_training_all_variables, newdata = attrition_cleansed_validation, type="response")
yhat_lr_all_variables <- (pred_lr_all_variables > 0.5) * 1
pred_lr_significant <- predict(lr_training_significant, newdata = attrition_cleansed_validation, type="response")
yhat_lr_significant <- (pred_lr_all_variables > 0.5) * 1
pred_lr_feeling1 <- predict(lr_training_feeling1, newdata = attrition_cleansed_validation, type="response")
yhat_lr_feeling1 <- (pred_lr_all_variables > 0.5) * 1
pred_lr_feeling2 <- predict(lr_training_feeling2, newdata = attrition_cleansed_validation, type="response")
yhat_lr_feeling2 <- (pred_lr_all_variables > 0.5) * 1
pred_lr_feeling3 <- predict(lr_training_feeling3, newdata = attrition_cleansed_validation, type="response")
yhat_lr_feeling3 <- (pred_lr_all_variables > 0.5) * 1

predicted_class_lr_all_variables <- data.frame(attrition_cleansed_validation$Attrition_Status, as.factor(yhat_lr_all_variables))
names(predicted_class_lr_all_variables) <-  c("yact", "yhat")
predicted_class_lr_significant <- data.frame(attrition_cleansed_validation$Attrition_Status, as.factor(yhat_lr_significant))
names(predicted_class_lr_significant) <-  c("yact", "yhat")
predicted_class_lr_feeling1 <- data.frame(attrition_cleansed_validation$Attrition_Status, as.factor(yhat_lr_feeling1))
names(predicted_class_lr_feeling1) <-  c("yact", "yhat")
predicted_class_lr_feeling2 <- data.frame(attrition_cleansed_validation$Attrition_Status, as.factor(yhat_lr_feeling2))
names(predicted_class_lr_feeling2) <-  c("yact", "yhat")
predicted_class_lr_feeling3 <- data.frame(attrition_cleansed_validation$Attrition_Status, as.factor(yhat_lr_feeling3))
names(predicted_class_lr_feeling3) <-  c("yact", "yhat")

cm_predicted_lr_all_variables <- confusionMatrix(predicted_class_lr_all_variables$yact, predicted_class_lr_all_variables$yhat, positive="1")
cm_predicted_lr_significant <- confusionMatrix(predicted_class_lr_all_variables$yact, predicted_class_lr_all_variables$yhat, positive="1")
cm_predicted_lr_feeling1 <- confusionMatrix(predicted_class_lr_all_variables$yact, predicted_class_lr_all_variables$yhat, positive="1")
cm_predicted_lr_feeling2 <- confusionMatrix(predicted_class_lr_all_variables$yact, predicted_class_lr_all_variables$yhat, positive="1")
cm_predicted_lr_feeling3 <- confusionMatrix(predicted_class_lr_all_variables$yact, predicted_class_lr_all_variables$yhat, positive="1")

cm_predicted_lr_all_variables
cm_predicted_lr_significant
cm_predicted_lr_feeling1
cm_predicted_lr_feeling2
cm_predicted_lr_feeling3
```

Summarizing the performance of the models' in terms of accuracy, sensitivity, and specificity:
```{r Logistic_Model_Performance}
print("Model 1")
cm_train_lr_training_all_variables$overall['Accuracy']
cm_train_lr_training_all_variables$byClass['Sensitivity']
cm_train_lr_training_all_variables$byClass['Specificity']
print("Model 2")
cm_train_lr_training_significant$overall['Accuracy']
cm_train_lr_training_significant$byClass['Sensitivity']
cm_train_lr_training_significant$byClass['Specificity']
print("Model 3")
cm_train_lr_training_feeling1$overall['Accuracy']
cm_train_lr_training_feeling1$byClass['Sensitivity']
cm_train_lr_training_feeling1$byClass['Specificity']
print("Model 4")
cm_train_lr_training_feeling2$overall['Accuracy']
cm_train_lr_training_feeling2$byClass['Sensitivity']
cm_train_lr_training_feeling2$byClass['Specificity']
print("Model 5")
cm_train_lr_training_feeling3$overall['Accuracy']
cm_train_lr_training_feeling3$byClass['Sensitivity']
cm_train_lr_training_feeling3$byClass['Specificity']

print("Model 1")
cm_predicted_lr_all_variables$overall['Accuracy']
cm_predicted_lr_all_variables$byClass['Sensitivity']
cm_predicted_lr_all_variables$byClass['Specificity']
print("Model 2")
cm_predicted_lr_significant$overall['Accuracy']
cm_predicted_lr_significant$byClass['Sensitivity']
cm_predicted_lr_significant$byClass['Specificity']
print("Model 3")
cm_predicted_lr_feeling1$overall['Accuracy']
cm_predicted_lr_feeling1$byClass['Sensitivity']
cm_predicted_lr_feeling1$byClass['Specificity']
print("Model 4")
cm_predicted_lr_feeling2$overall['Accuracy']
cm_predicted_lr_feeling2$byClass['Sensitivity']
cm_predicted_lr_feeling2$byClass['Specificity']
print("Model 5")
cm_predicted_lr_feeling3$overall['Accuracy']
cm_predicted_lr_feeling3$byClass['Sensitivity']
cm_predicted_lr_feeling3$byClass['Specificity']
```

#### Fitting a decision tree model

```{r Decision_Tree_Libraries}
library(rpart)
library(rpart.plot)
```

```{r Decision_Tree_Training}
decision_tree_training_all_variables <- rpart(Attrition_Status ~ Experience_in_Months + Employee_Age + Extraversion + Agreeableness + Conscientiousness + Neuroticism + Openness + Gender + Employee_Profession + Employee_Industry + Source_of_Hire + Coach + Head_Supervisor_Gender + Way_to_Work + Wage_Color,
                                              data=attrition_cleansed_training)
decision_tree_training_significant <- rpart(Attrition_Status ~ Experience_in_Months + Source_of_Hire + Way_to_Work,
                                              data=attrition_cleansed_training)
decision_tree_training_feeling1 <- rpart(Attrition_Status ~ Experience_in_Months + Employee_Profession + Employee_Industry + Source_of_Hire + Way_to_Work,
                                              data=attrition_cleansed_training)
decision_tree_training_feeling2 <- rpart(Attrition_Status ~ Experience_in_Months + Extraversion + Agreeableness + Conscientiousness + Employee_Profession + Employee_Industry + Source_of_Hire + Way_to_Work,
                                              data=attrition_cleansed_training)
decision_tree_training_feeling3 <- rpart(Attrition_Status ~ Experience_in_Months + Employee_Age + Extraversion + Agreeableness + Conscientiousness + Neuroticism + Gender + Employee_Profession + Employee_Industry + Source_of_Hire + Way_to_Work + Wage_Color,
                                              data=attrition_cleansed_training)

fitted_tree_training_all_variables <- predict(decision_tree_training_all_variables, type="class")
fitted_tree_training_significant <- predict(decision_tree_training_significant, type="class")
fitted_tree_training_feeling1 <- predict(decision_tree_training_feeling1, type="class")
fitted_tree_training_feeling2 <- predict(decision_tree_training_feeling2, type="class")
fitted_tree_training_feeling3 <- predict(decision_tree_training_feeling3, type="class")

cm_tree_training_all_variables <- confusionMatrix(fitted_tree_training_all_variables, attrition_cleansed_training$Attrition_Status, positive="1")
cm_tree_training_significant <- confusionMatrix(fitted_tree_training_significant, attrition_cleansed_training$Attrition_Status, positive="1")
cm_tree_training_feeling1 <- confusionMatrix(fitted_tree_training_feeling1, attrition_cleansed_training$Attrition_Status, positive="1")
cm_tree_training_feeling2 <- confusionMatrix(fitted_tree_training_feeling2, attrition_cleansed_training$Attrition_Status, positive="1")
cm_tree_training_feeling3 <- confusionMatrix(fitted_tree_training_feeling3, attrition_cleansed_training$Attrition_Status, positive="1")

cm_tree_training_all_variables
cm_tree_training_significant
cm_tree_training_feeling1
cm_tree_training_feeling2
cm_tree_training_feeling3
```

Making predictions on the validation set data:
```{r tree1_test}
predicted_tree_all_variables <- predict(decision_tree_training_all_variables, newdata = attrition_cleansed_validation, type = "class")
predicted_tree_significant <- predict(decision_tree_training_significant, newdata = attrition_cleansed_validation, type = "class")
predicted_tree_feeling1 <- predict(decision_tree_training_feeling1, newdata = attrition_cleansed_validation, type = "class")
predicted_tree_feeling2 <- predict(decision_tree_training_feeling2, newdata = attrition_cleansed_validation, type = "class")
predicted_tree_feeling3 <- predict(decision_tree_training_feeling3, newdata = attrition_cleansed_validation, type = "class")

cm_tree_all_variables <- confusionMatrix(predicted_tree_all_variables, attrition_cleansed_validation$Attrition_Status, positive="1")
cm_tree_significant <- confusionMatrix(predicted_tree_significant, attrition_cleansed_validation$Attrition_Status, positive="1")
cm_tree_feeling1 <- confusionMatrix(predicted_tree_feeling1, attrition_cleansed_validation$Attrition_Status, positive="1")
cm_tree_feeling2 <- confusionMatrix(predicted_tree_feeling2, attrition_cleansed_validation$Attrition_Status, positive="1")
cm_tree_feeling3 <- confusionMatrix(predicted_tree_feeling3, attrition_cleansed_validation$Attrition_Status, positive="1")

cm_tree_all_variables
cm_tree_significant
cm_tree_feeling1
cm_tree_feeling2
cm_tree_feeling3
```

Summarizing the performance of the models' in terms of accuracy, sensitivity, and specificity:
```{r}
print("Model 1")
cm_tree_training_all_variables$overall['Accuracy']
cm_tree_training_all_variables$byClass['Sensitivity']
cm_tree_training_all_variables$byClass['Specificity']
print("Model 2")
cm_tree_training_significant$overall['Accuracy']
cm_tree_training_significant$byClass['Sensitivity']
cm_tree_training_significant$byClass['Specificity']
print("Model 3")
cm_tree_training_feeling1$overall['Accuracy']
cm_tree_training_feeling1$byClass['Sensitivity']
cm_tree_training_feeling1$byClass['Specificity']
print("Model 4")
cm_tree_training_feeling2$overall['Accuracy']
cm_tree_training_feeling2$byClass['Sensitivity']
cm_tree_training_feeling2$byClass['Specificity']
print("Model 5")
cm_tree_training_feeling3$overall['Accuracy']
cm_tree_training_feeling3$byClass['Sensitivity']
cm_tree_training_feeling3$byClass['Specificity']

print("Model 1")
cm_tree_all_variables$overall['Accuracy']
cm_tree_all_variables$byClass['Sensitivity']
cm_tree_all_variables$byClass['Specificity']
print("Model 2")
cm_tree_significant$overall['Accuracy']
cm_tree_significant$byClass['Sensitivity']
cm_tree_significant$byClass['Specificity']
print("Model 3")
cm_tree_feeling1$overall['Accuracy']
cm_tree_feeling1$byClass['Sensitivity']
cm_tree_feeling1$byClass['Specificity']
print("Model 4")
cm_tree_feeling2$overall['Accuracy']
cm_tree_feeling2$byClass['Sensitivity']
cm_tree_feeling2$byClass['Specificity']
print("Model 5")
cm_tree_feeling3$overall['Accuracy']
cm_tree_feeling3$byClass['Sensitivity']
cm_tree_feeling3$byClass['Specificity']
```

#### Fitting random forests

```{r Random_Forest_Library}
library(randomForest)
```
```{r Random_Forests}
set.seed(100)
forest_training_all_variables <- randomForest(Attrition_Status ~ Experience_in_Months + Employee_Age + Extraversion + Agreeableness + Conscientiousness + Neuroticism + Openness + Gender + Employee_Profession + Employee_Industry + Source_of_Hire + Coach + Head_Supervisor_Gender + Way_to_Work + Wage_Color,
                                        data = attrition_cleansed_training, importance=TRUE, na.action = na.omit)
forest_training_significant <- randomForest(Attrition_Status ~ Experience_in_Months + Source_of_Hire + Way_to_Work,
                                        data = attrition_cleansed_training, importance=TRUE, na.action = na.omit)
forest_training_feeling1 <- randomForest(Attrition_Status ~ Experience_in_Months + Employee_Profession + Employee_Industry + Source_of_Hire + Way_to_Work,
                                        data = attrition_cleansed_training, importance=TRUE, na.action = na.omit)
forest_training_feeling2 <- randomForest(Attrition_Status ~ Experience_in_Months + Extraversion + Agreeableness + Conscientiousness + Employee_Profession + Employee_Industry + Source_of_Hire + Way_to_Work,
                                        data = attrition_cleansed_training, importance=TRUE, na.action = na.omit)
forest_training_feeling3 <- randomForest(Attrition_Status ~ Experience_in_Months + Employee_Age + Extraversion + Agreeableness + Conscientiousness + Neuroticism + Gender + Employee_Profession + Employee_Industry + Source_of_Hire + Way_to_Work + Wage_Color,
                                        data = attrition_cleansed_training, importance=TRUE, na.action = na.omit)

forest_training_all_variables
forest_training_significant
forest_training_feeling1
forest_training_feeling2
forest_training_feeling3

#Summarizing the training models' performance in terms of accuracy, sensitivity, and specificity.
print("Model 1")
# Accuracy
print("Accuracy:")
(236 + 286)/(236 + 154 + 109 + 286)
# Sensitivity
print("Sensitivity:")
286/(286 + 154)
# Specificity
print("Specificity:")
236/(236 + 109)

print("Model 2")
# Accuracy
print("Accuracy:")
(215 + 235)/(215 + 175 + 160 + 235)
# Sensitivity
print("Sensitivity:")
235/(235 + 175)
# Specificity
print("Specificity:")
215/(215 + 160)

print("Model 3")
# Accuracy
print("Accuracy:")
(235 + 286)/(235 + 155 + 109 + 286)
# Sensitivity
print("Sensitivity:")
286/(286 + 155)
# Specificity
print("Specificity:")
235/(235 + 109)

print("Model 4")
# Accuracy
print("Accuracy:")
(224 + 284)/(224 + 166 + 111 + 284)
# Sensitivity
print("Sensitivity:")
284/(284 + 166)
# Specificity
print("Specificity:")
224/(224 + 111)

print("Model 5")
# Accuracy
print("Accuracy:")
(239 + 281)/(239 + 151 + 114 + 281)
# Sensitivity
print("Sensitivity:")
281/(281 + 151)
# Specificity
print("Specificity:")
239/(239 + 114)

#Making predictions on the validation set data:
prediction_forest_all_variables <- predict(forest_training_all_variables, newdata = attrition_cleansed_validation, type = "class")
confusion_prediction_forest_all_variables <- confusionMatrix(prediction_forest_all_variables, attrition_cleansed_validation$Attrition_Status, positive = "1")
prediction_forest_significant <- predict(forest_training_significant, newdata = attrition_cleansed_validation, type = "class")
confusion_prediction_forest_significant <- confusionMatrix(prediction_forest_significant, attrition_cleansed_validation$Attrition_Status, positive = "1")
prediction_forest_feeling1 <- predict(forest_training_feeling1, newdata = attrition_cleansed_validation, type = "class")
confusion_prediction_forest_feeling1 <- confusionMatrix(prediction_forest_feeling1, attrition_cleansed_validation$Attrition_Status, positive = "1")
prediction_forest_feeling2 <- predict(forest_training_feeling2, newdata = attrition_cleansed_validation, type = "class")
confusion_prediction_forest_feeling2 <- confusionMatrix(prediction_forest_feeling2, attrition_cleansed_validation$Attrition_Status, positive = "1")
prediction_forest_feeling3 <- predict(forest_training_feeling3, newdata = attrition_cleansed_validation, type = "class")
confusion_prediction_forest_feeling3 <- confusionMatrix(prediction_forest_feeling3, attrition_cleansed_validation$Attrition_Status, positive = "1")

#Summarizing the validation models' performance in terms of accuracy, sensitivity, and specificity.
print("Model 1")
confusion_prediction_forest_all_variables$overall['Accuracy']
confusion_prediction_forest_all_variables$byClass['Sensitivity']
confusion_prediction_forest_all_variables$byClass['Specificity']
print("Model 2")
confusion_prediction_forest_significant$overall['Accuracy']
confusion_prediction_forest_significant$byClass['Sensitivity']
confusion_prediction_forest_significant$byClass['Specificity']
print("Model 3")
confusion_prediction_forest_feeling1$overall['Accuracy']
confusion_prediction_forest_feeling1$byClass['Sensitivity']
confusion_prediction_forest_feeling1$byClass['Specificity']
print("Model 4")
confusion_prediction_forest_feeling2$overall['Accuracy']
confusion_prediction_forest_feeling2$byClass['Sensitivity']
confusion_prediction_forest_feeling2$byClass['Specificity']
print("Model 5")
confusion_prediction_forest_feeling3$overall['Accuracy']
confusion_prediction_forest_feeling3$byClass['Sensitivity']
confusion_prediction_forest_feeling3$byClass['Specificity']
```
